---
title: "EDA"
format: pdf
editor: visual
---

# Introduction:


# Illistration:


# Background and Related Works:


# Data Processing:
We loaded in the datasets though the readxl package
```{r}
library(readxl)
library(tidyverse)

df <- read_excel('smartphones_-_smartphones.xlsx')
#df2 <-
```



## First Dataset
The first data set looked like this before processing.
```{r}
head(df)
```



To start for the fisrt we took out the model column because it represented the names of the phones which will not impact the price.  We also took out the sim column.
```{r}
df <- df %>% drop_na() %>% select(!model) %>% select(!sim)
```



### Cleaning battery column
We extracted the battery life of each phone in mAH and made the column numeric
```{r}
df <- df %>% 
  mutate(battery = gsub(pattern = "mAh Battery|with|(?:[0-9]){1,3}W|Fast Charging", replacement = "", battery)) %>% mutate_at('battery', as.numeric) %>% drop_na() %>% rename('battery (mAh)'='battery')
```


### Cleaning processor variable
We extracted the power of the processor in GHz.  We then made the column numeric
```{r}
df$processor <- str_extract(df$processor, "\\d+\\.?\\d*\\s*GHz|\\d+\\s*GHz")

df$processor <- gsub("GHz", "", df$processor)

df <- df %>% drop_na() %>% mutate_at('processor', as.numeric) %>%rename('processor (GHz)'='processor')
```


### Cleaning os column
We noticed that because the data was unclean, some of the values that should be in the os column were in the card column.  We put these value in the os column and removed the card column after.  We also made the os column a factor.
```{r}
for (i in 1:nrow(df)){
  if (df[i,9] == 'No FM Radio'){
    df[i,9] <- df[i,8]
  }
  else if (df[i,9] == 'Bluetooth'){
    df[i,9] <- df[i,8]
  }
}

df <- df %>% select(!card) %>% mutate_at('os', as.factor)  
```


### Cleaning camera column
We extracted the amount of mega pixels in the front camera of each phone.  We made this column numeric
```{r}
df$camera <- str_extract(df$camera, '[0-9]{1,2} MP Front Camera')
df$camera <- str_extract(df$camera, '[0-9]{1,2}')
df <- df %>% mutate_at('camera', as.numeric) %>% rename('f camera MP'='camera') %>% drop_na()
```

### Cleaning ram column
We extracted the ram of the phones in GB and made it a factor because phones only have a few preset values for their ram
```{r}
df$ram <- str_extract(df$ram, '[0-9]{1,2} GB RAM')
#df$ram <- str_extract(df$ram, '[0-9]{1,2}')
df <- df %>% mutate_at('ram', as.factor) %>% rename('ram (GB)'='ram')
```


### Cleaning Display column
We extracted the display size and the Hz of the display and turned that into two new columns.  We made these new columns numeric and removed the original 
```{r}
df <- df %>% mutate(displaySize = as.numeric(str_extract(df$display, "\\b\\d+\\.\\d+\\b")))
```


```{r}
df <- df %>% mutate(displayHz = as.numeric(str_extract(df$display, "\\b\\d+(?=\\s*Hz)")))

df <- df %>% select(!display)
```



### Cleaning Price column
We converted the value in rupees to dollars to make it easier to understand for our audience
```{r}
df <- df %>%
  mutate(price = gsub(",", "", price))
df$price <- sub("\\₹", "", df$price)
df$price <- as.numeric(df$price)

df <- df %>%
  mutate(price = round(price / 83.41, digits = 2))
```

### General Analysis
```{r}
summary(df)
```



## Second Dataset








